---
title: "Introduction to r2dii.analysis" 
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

## Load your r2dii libraries

The first step in your analysis will be to load in the recommended r2dii packages into your current R session. [r2dii.data](https://2degreesinvesting.github.io/r2dii.data) includes fake data to help demonstrate the tool and [r2dii.match](https://2degreesinvesting.github.io/r2dii.match) provides functions to help you easily match your loanbook to asset-level data.

``` {r use-r2dii}
library(r2dii.data)
library(r2dii.match)
library(r2dii.analysis)
```

We also recommend packages in the [tidyverse](https://www.tidyverse.org/); they are optional but useful.

``` {r use-tidyverse}
library(tidyverse)
```

## Match your loanbook to climate-related asset-level data

See [r2dii.match](https://2degreesinvesting.github.io/r2dii.match) for a more complete description of this process. 

```{r match}
# Use these datasets to practice but eventually you should use your own data.
# The optional syntax `package::data` is to clarify where the data comes from.
loanbook <- r2dii.data::loanbook_demo
ald <- r2dii.data::ald_demo

matched <- match_name(loanbook, ald) %>% prioritize()

matched
```

## Calculate targets

You can calculate scenario targets using two different approaches: Market Share Approach, or Sectoral Decarbonization Approach.

### Market Share Approach

The [Market Share Approach](https://2degreesinvesting.github.io/r2dii.analysis/articles/target-sda.html) is used to calculate scenario targets for the `production` of a technology in a sector. For example, we can use this approach to set targets for the production of electric vehicles in the automotive sector. This approach is recommended for sectors where a granular technology scenario roadmap exists.

Targets can be set at the portfolio level:

```{r market-share-targets-portfolio}
# Use these datasets to practice but eventually you should use your own data.
scenario <- r2dii.data::scenario_demo_2020
regions <- r2dii.data::region_isos_demo

market_share_targets_portfolio <- matched %>%
  target_market_share(
    ald = ald,
    scenario = scenario,
    region_isos = regions
  )

market_share_targets_portfolio
```

Or at the company level: 

```{r market-share-targets-company}
market_share_targets_company <- matched %>%
  target_market_share(
    ald = ald,
    scenario = scenario,
    region_isos = regions,
    # Output results at company-level.
    by_company = TRUE 
  )

market_share_targets_company
```

### Sectoral Decarbonization Approach

The [Sectoral Decarbonization Approach](https://2degreesinvesting.github.io/r2dii.analysis/articles/target-market-share.html) is used to calculate scenario targets for the `emission_factor` of a sector. For example, you can use this approach to set targets for the average emission factor of the cement sector. This approach is recommended for sectors lacking technology roadmaps.

```{r sda-targets}
# Use this dataset to practice but eventually you should use your own data.
co2 <- r2dii.data::co2_intensity_scenario_demo

sda_targets <- matched %>%
  target_sda(ald = ald, co2_intensity_scenario = co2)

sda_targets
```

## Visualization

There are a large variety of possible visualizations stemming from the outputs of `target_market_share()` and `target_sda()`. Below, we have highlighted a couple of common plots, along with the minimum code necessary to reproduce them.

### Market Share: Sector-level technology mix

From the market share output, you can plot the portfolio's exposure to various climate sensitive technologies (`projected`), and compare with various scenario targets.

```{r technoloy mix portfolio}
# Pick the targets you want to plot.
tech_mix_data <- market_share_targets_portfolio %>%
  filter(
    sector == "power",
    weighted_production_metric != "normalized_corporate_economy",
    year == max(year)
  )

ggplot(
  data = tech_mix_data, 
  mapping = aes(
    x = weighted_production_metric, 
    y = weighted_production_value, 
    fill = technology
  )
) +
  geom_col(position = "fill") +
  labs(x = "Metric", y = "Weighted Capacity [%]")
```

### Market Share: Technology-level volume trajectory

You can also plot the technology-specific volume trend. All targets and benchmarks are normalized to the initial portfolio value, so we are effectively comparing ambition.

```{r volume portfolio}
renewables_data <- filter(
  market_share_targets_portfolio,
  sector == "power",
  technology == "renewablescap",
  region == "global"
)

just_targets2 <- renewables_data %>%
  filter(str_detect(weighted_production_metric, "target_"))

ceiling <- just_targets %>%
  group_by(sector, technology, year, region, scenario_source) %>%
  summarize(
    weighted_production_metric = "target_ceiling",
    weighted_production_value = max(weighted_production_value)
  ) %>%
  group_by(sector, technology, region, scenario_source) %>%
  mutate(weighted_production_value = max(weighted_production_value))

just_data <- renewables_data %>%
  filter(!str_detect(weighted_production_metric, "target_"))

targets_and_ceiling <- just_targets %>%
  rbind(ceiling) %>%
  group_by(year) %>%
  arrange(year, weighted_production_value) %>%
  mutate(
    previous_value = lag(weighted_production_value, default = 0),
  ) %>%
  filter(region == "global")

ggplot(
  data = targets_and_ceiling,
  mapping = aes(
    x = year,
    y = weighted_production_value,
    fill = weighted_production_metric
  )
) +
  geom_ribbon(
    data = targets_and_ceiling,
    mapping = aes(ymin = previous_value, ymax = weighted_production_value)
  ) +
  geom_line(
    data = just_data, 
    mapping = aes(
      x = year, 
      y = weighted_production_value, 
      linetype = weighted_production_metric
    )
  ) +
  facet_wrap(vars(sector, technology))
```

### SDA Target

From the SDA output, we can compare the projected average emission intensity attributed to the portfolio, with the actual emission intensity scenario, and the scenario compliant SDA pathway that the portfolio must follow to achieve the scenario ambition by 2050.

```{r sda plot}
ggplot(
  data = sda_targets, 
  mapping = aes(
    x = year, 
    y = emission_factor_value, 
    color = emission_factor_metric)
) +
  geom_line() +
  facet_wrap(~ sector)
```
