---
title: "Introduction to r2dii.analysis" 
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

## Load your r2dii libraries

The first step in your analysis will be to load in the recommended r2dii 
packages into your current R session.
[r2dii.data](https://rmi-pacta.github.io/r2dii.data) includes fake data 
to help demonstrate the tool and 
[r2dii.match](https://rmi-pacta.github.io/r2dii.match) provides 
functions to help you easily match your loanbook to asset-level data.

``` {r use-r2dii}
library(r2dii.data)
library(r2dii.match)
library(r2dii.analysis)
```

To plot your results, you may also load the package 
[r2dii.plot](https://rmi-pacta.github.io/r2dii.plot).

``` {r use-r2dii.plot}
library(r2dii.plot)
```

We also recommend packages in the [tidyverse](https://www.tidyverse.org/); they 
are optional but useful.

``` {r use-tidyverse}
library(tidyverse)
```

## Match your loanbook to climate-related asset-level data

See [r2dii.match](https://rmi-pacta.github.io/r2dii.match) for a more 
complete description of this process. 

```{r matched}
# Use these datasets to practice but eventually you should use your own data.
# The optional syntax `package::data` is to clarify where the data comes from.
loanbook <- r2dii.data::loanbook_demo
abcd <- r2dii.data::abcd_demo

matched <- match_name(loanbook, abcd) %>% prioritize()

matched
```

## Calculate targets

You can calculate scenario targets using two different approaches: Market Share 
Approach, or Sectoral Decarbonization Approach.

### Market Share Approach

The [Market Share Approach](https://rmi-pacta.github.io/r2dii.analysis/articles/target-market-share.html) is used to calculate scenario targets for the 
`production` of a technology in a sector. For example, we can use this approach 
to set targets for the production of electric vehicles in the automotive sector. 
This approach is recommended for sectors where a granular technology scenario 
roadmap exists.

Targets can be set at the portfolio level:

```{r market-share-targets-portfolio}
# Use these datasets to practice but eventually you should use your own data.
scenario <- r2dii.data::scenario_demo_2020
regions <- r2dii.data::region_isos_demo

market_share_targets_portfolio <- matched %>%
  target_market_share(
    abcd = abcd,
    scenario = scenario,
    region_isos = regions
  )

market_share_targets_portfolio
```

Or at the company level: 

```{r market-share-targets-company}
market_share_targets_company <- matched %>%
  target_market_share(
    abcd = abcd,
    scenario = scenario,
    region_isos = regions,
    # Output results at company-level.
    by_company = TRUE 
  )

market_share_targets_company
```

### Sectoral Decarbonization Approach

The [Sectoral Decarbonization Approach](https://rmi-pacta.github.io/r2dii.analysis/articles/target-sda.html) 
is used to calculate scenario targets for the `emission_factor` of a sector. For
example, you can use this approach to set targets for the average emission 
factor of the cement sector. This approach is recommended for sectors lacking 
technology roadmaps.

```{r sda-targets}
# Use this dataset to practice but eventually you should use your own data.
co2 <- r2dii.data::co2_intensity_scenario_demo

sda_targets <- matched %>%
  target_sda(abcd = abcd, co2_intensity_scenario = co2, region_isos = regions) %>% 
  filter(sector == "cement", year >= 2020)

sda_targets
```

## Visualization

There are a large variety of possible visualizations stemming from the outputs 
of `target_market_share()` and `target_sda()`. Below, we highlight a couple of 
common plots that can easily be created using the `r2dii.plot` package.

### Market Share: Sector-level technology mix

From the market share output, you can plot the portfolio's exposure to various 
climate sensitive technologies (`projected`), and compare with the corporate 
economy, or against various scenario targets.

```{r technoloy-mix-portfolio}
# Pick the targets you want to plot.
data <- filter(
  market_share_targets_portfolio,
  scenario_source == "demo_2020",
  sector == "power",
  region == "global",
  metric %in% c("projected", "corporate_economy", "target_sds")
)

# Plot the technology mix
qplot_techmix(data)
```

### Market Share: Technology-level volume trajectory

You can also plot the technology-specific volume trend. All starting values are
normalized to 1, to emphasize that we are comparing the rates of buildout and/or
retirement. 

```{r trajetory-portfolio}
data <- filter(
  market_share_targets_portfolio,
  sector == "power",
  technology == "renewablescap",
  region == "global",
  scenario_source == "demo_2020"
)

qplot_trajectory(data)
```

### SDA Target

From the SDA output, we can compare the projected average emission intensity 
attributed to the portfolio, with the actual emission intensity scenario, and 
the scenario compliant SDA pathway that the portfolio must follow to achieve 
the scenario ambition by 2050.

```{r sda plot}
data <- filter(sda_targets, sector == "cement", region == "global")
qplot_emission_intensity(data)
```
