---
title: "Market Share Approach"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of this article is to define the _market-share-approach_ for allocating scenario efforts and to show how to calculate the market-share target for a given scenario.

## Scenario market-shares

Say that you want to study how a portfolio would perform in a specific climate scenario. How can you allocate scenario efforts to the production profile of your portfolio? You can do that in two ways -- by technology, or by sector.

### 1. Market-share by technology
We define the market-share by technology as: 

$$p_{i}^{tmsr}(t) = p_{i}(t_{0}) +  p_{i}(t_{0}) * \frac{s_i(t) - s_{i}(t_0)}{s_i(t_0)}$$

We can see that this reduces to:

$$p_{i}^{tmsr}(t) = p_{i}(t_{0}) \left(1 + \frac{s_i(t) - s_{i}(t_0)}{s_i(t_0)} \right) \\
p_{i}^{tmsr}(t) = p_{i}(t_{0}) \left(1 + \frac{s_i(t)}{s_i(t_0)} -1 \right) \\
p_{i}^{tmsr}(t) = p_{i}(t_{0}) * \frac{s_i(t)}{s_i(t_0)}$$

where:

* $s_i(t)$ is the scenario production for technology $i$ at time $t$,
* $p_{i}(t_0)$ is the production allocated to the portfolio for some technology, $i$ at time $t_0$, and
* $p_{i}^{tmsr}(t)$ is the portfolio-specific target production for that technology.

We define the "Technology Market Share Ratio" as:

$$\dfrac{s_i(t)}{s_i(t_0)}$$
This method is used to set targets for "decreasing" (ie. brown) technologies. 

### 2. Market-share by sector
To calculate the market-share by sector, we use the initial production of both the portfolio and scenario at the sector-level instead. 
$$p_{i}^{smsp}(t) = p_{i}(t_0) +P(t_0) * \left( \dfrac{s_i(t)-s_i(t_0)}{S(t_0)}\right)$$
where:

* $P_i(t_0)$ is the portfolio's total production in the sector at $t_0$, and
* $S(t_0)$ is the scenario total production at $t_0$.

We define the "Sector Market Share Percentage" as:

$$\dfrac{s_i(t)-s_i(t_0)}{S(t_0)}$$
This method is used to calculate targets for "increasing" (ie. green) technologies. 

## How to calculate market-share targets for a given scenario

To calculate market-share targets, you need to use the package r2dii.analysis and a number of datasets. One of those datasets is a "matched" dataset (loanbook + asset-level data) that you can get with the package [r2dii.match](https://2degreesinvesting.github.io/r2dii.match/). The datasets I use here come from the package [r2dii.data](https://2degreesinvesting.github.io/r2dii.data/); they are fake but show how you should structure your own data.

* Use packages.

```{r}
library(r2dii.data)
library(r2dii.match)
library(r2dii.analysis)
```

* Match the loanbook to asset level data.

```{r}
loanbook <- r2dii.data::loanbook_demo
ald <- r2dii.data::ald_demo

matched <- match_name(loanbook, ald) %>%
  # WARNING: Remember to validate the output of match_name() before prioritize()
  prioritize()

matched
```

* Calculate market-share targets for production at the portfolio level.

```{r}
# portfolio level targets
scenario <- r2dii.data::scenario_demo_2020
regions <- r2dii.data::region_isos_demo


matched %>% target_market_share(ald, scenario, regions)
```

* Calculate market-share targets for production at the company level.

```{r}
matched %>% target_market_share(ald, scenario, regions, by_company = TRUE)
```
