---
title: "Market Share Approach"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(r2dii.data)
library(r2dii.analysis)
```

## Scenario Market Shares

Scenario efforts must be allocated to the portfolio's production profile. To do this, two principles are currently implemented:

1. Technology Market Share:

$$p_{i}^{tmsr}(t) = p_{i}(t_0) * \dfrac{s_i(t)}{s_i(t_0)}$$

where:

* $s_i(t)$ is the scenario production for technology $i$ at time $t$,
* $p_{i}(t_0)$ is the production allocated to the portfolio for some technology, $i$ at time $t_0$, and
* $p_{i}^{tmsr}(t)$ is the portfolio-specific target production for that technology.

We define the "Technology Market Share Ratio" as:

$$\dfrac{s_i(t)}{s_i(t_0)}$$

2. Sector Market Share:

$$p_{i}^{smsp}(t) = p_{i}(t_0) +P(t_0) * \left( \dfrac{s_i(t)-s_i(t_0)}{S(t_0)}\right)$$
where:

* $P_i(t_0)$ is the portfolio's total production in the sector at $t_0$, and
* $S(t_0)$ is the scenario total production at $t_0$.

We define the "Sector Market Share Percentage" as:

$$\dfrac{s_i(t)-s_i(t_0)}{S(t_0)}$$

## Calculating Market Share Targets

To calculate Market Share Targets, you need to use the package r2dii.analysis and a number of datasets, including a "matched" dataset (loanbook + asset-level data) that you can get with the package [r2dii.match](https://2degreesinvesting.github.io/r2dii.match/). The datasets I use here come from the package [r2dii.data](https://2degreesinvesting.github.io/r2dii.data/); they are fake but show how you should structure your own data.

* Use packages.

```{r}
library(r2dii.data)
library(r2dii.match)
library(r2dii.analysis)
```

* Match the loanbook to asset level data.

```{r}
loanbook <- r2dii.data::loanbook_demo
ald <- r2dii.data::ald_demo

matched <- match_name(loanbook, ald) %>% 
  # WARNING: Remember to validate the output of match_name() before prioritize()
  prioritize()

matched
```

* Calculate Market Share targets for production.

```{r}
production_scenario <- r2dii.data::scenario_demo_2020

# portfolio level targets
matched %>% 
  join_ald_scenario(ald, 
                    production_scenario,
                    region_isos = region_isos_demo) %>%
  summarize_portfolio_production() %>% 
  target_market_share_portfolio()

# company level targets
matched %>% 
  join_ald_scenario(ald, 
                    production_scenario,
                    region_isos = region_isos_demo) %>%
  summarize_company_production() %>% 
  target_market_share_company()
```

